### 2018-05-23 VV570/HW1/assignment.tex
add ex1, 7

@@

\section{Metric Space}

@@

			Thus, $\{f(v_1), f(v_2), ... , f(v_n)\}$ forms the basis of $V_2$, and the dimension of $V_2$ is therefore $n$. The rank-nullity theorem written as below is proved.
			\begin{equation}
				dim(V_1) = dim(ker(f)) + dim(V_2)
			\end{equation}
		\end{proof}
	\item
		\begin{proof}

		\end{proof}
	\item
		\begin{proof}

>>>>

\usepackage{algorithm, algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}} %Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm

\usepackage{listings}
\lstset{language=Matlab}

@@

\section{Metric Space}
\begin{enumerate}
	\item
		\begin{proof}
			Since there's no elements in $\emptyset$, so $\emptyset$ is open, as $X^\complement = \emptyset$, so $X$ is closed.\\
			$X$ is open as it contains all the elemnets, since $\emptyset^\complement = X$, thus $\emptyset$ is closed. 
		\end{proof}
	\item
		\begin{proof}
			Since
			\begin{equation}
				T \triangleq (U_1 \cap U_2 \cap ... \cap U_m)^\complement = U_1^\complement \cup U_2^\complement \cup ... \cup U_m^\complement
			\end{equation}
			And ${U_i}^\complement$ is open, as $U_i$ is closed.\\
			Thus, $T$ is open, and therefore the intersection is closed. 
		\end{proof}
	\item 
		\begin{proof}
			Since
			\begin{equation}
				T \triangleq (U_1 \cup U_2 \cup ... \cup U_m)^\complement = U_1^\complement \cap U_2^\complement \cap ... \cap U_m^\complement
			\end{equation}
			And ${U_i}^\complement$ is open, as $U_i$ is closed.\\
			Thus, $T$ is open, and therefore the intersection is closed. 
		\end{proof}

\end{enumerate}

@@

			Thus, $\{f(v_1), f(v_2), ... , f(v_n)\}$ forms the basis of $V_2$, and the dimension of $V_2$ is therefore $n$. The rank-nullity theorem written as below is proved.
			\begin{equation}
				dim(V_1) = dim(ker(f)) + dim(V_2)
			\end{equation}
		\end{proof}

	\item
		\begin{proof}
			Let $U, V, W$ be vector spaces over the same field $K$, function $f$ be a linear map from $U$ to $V$ and function $g$ be a linear map from $V$ to $W$. It's left to show that the composition of $f$ and $g$, denoted as $h$, which maps a vector in $U$ to $W$, is still a linear map.

			Given $u_1, u_2 \in U$ and any scalar $c \in \mathbb{K}$, then
			\begin{equation}
				\begin{aligned}
					h(u_1 + u_2) & = g(f(u_1 + u_2)) \\
								 & = g(f(u_1) + f(u_2)) \\
								 & = g(f(u_1)) + g(f(u_2)) \\
								 & = h(u_1) + h(u_2)
				\end{aligned}
			\end{equation}

			\begin{equation}
				\begin{aligned}
					h(c u_1) & = g(f(c u_1)) \\
							 & = g(c f(u_1)) \\
						     & = c g(f(u_1)) \\
							 & = c h(u_1)
				\end{aligned}
			\end{equation}

			Thus, the composition of two linear maps is still a linear map.
		\end{proof}

	\item
		\begin{proof}
			Let $U, V$ be vector spaces over the same field $K$, function $f$ be linear maps from $U$ to $V$. It's left to show that the inverse of $f$, denoted as $f^{-1}$, which maps a vector in $V$ to $U$ is still a linear map.

			By inverse, it means that
			\begin{equation}
				f(f^{-1}(x)) = f^{-1}(f(x)) = x
			\end{equation}

			Given $u_1, u_2 \in U$ and any scalar $c \in \mathbb{K}$, denote the counterpart of $u_1, u_2$ in $V$ as $v_1, v_2$ under the linear mapping function $f$. Then

			\begin{equation}
				\begin{aligned}
					f^{-1}(v_1 + v_2) & = f^{-1}(f(u_1) + f(u_2)) \\
									  & = f^{-1}(f(u_1 + u_2)) \\
									  & = u_1 + u_2 \\
									  & = f^{-1}(v_1) + f^{-1}(v_2)
				\end{aligned}
			\end{equation}

			\begin{equation}
				\begin{aligned}
					f^{-1}(c v_1) & = f^{-1}(c f(u_1)) \\
							      & = f^{-1}(f(c u_1)) \\
								  & = c u_1 \\
								  & = c f^{-1}(v_1)
				\end{aligned}
			\end{equation}

			Thus, the inverse of a linear map is still a linear map.
		\end{proof}
\end{enumerate}

%----------------------------------------------------------------------------------------
%	PROBLEM 6
%----------------------------------------------------------------------------------------

\section{Discontinuous linear maps}
\begin{enumerate}
	\item 
		\begin{proof}
			The $k$ times derivative of $f_n(x)$ can be written as below.
			\begin{equation}
				f_n^{(k)}(x) = n^{k-1} sin(nx+ \frac{k\pi}{2}) \ \ \ \ k = 0, 1, 2, 3, ...
			\end{equation}
			It's clear that $f_n^{(k)}(x)$ is continous for any $k$, thus $f_n(x) \in C^\infty(\mathbb{R})$.
		\end{proof}
	\item 
		\begin{equation}
			d f_n(x) = cos(nx) dx
		\end{equation}
	\item
		\begin{proof}
			Let $x_0 = 0, x_1 = \frac{\pi}{2n}$, then
			\begin{equation}
				\lim\limits_{n->+\infty} \vert x_1-x_0 \vert = 0
			\end{equation}
			\begin{equation}
				\lim\limits_{n->+\infty} \vert df_n(x_1) - df_n(x_0) \vert = \vert 0-dx \vert = |dx| \neq 0
			\end{equation}
			Thus, the differential is not continous when n tends to infty.
		\end{proof}
	\item 
		Sorry, haven't figured out yet...

\end{enumerate}

%----------------------------------------------------------------------------------------
%	PROBLEM 7
%----------------------------------------------------------------------------------------

\section{pi}
\begin{enumerate}
	\item 
		The main program(see Algorithm\ref{machin}) adopts Machin's formula to calculate $\pi$.
		\begin{equation}
			\pi = 4[4atan(\frac{1}{5}) - atan(\frac{1}{239})]
		\end{equation}

		Subroutine(see Algorithm\ref{atan_inv}) calculating $atan(\frac{1}{x})$ is used by the main program. Since
		\begin{equation}
			atan(x) = \frac{1}{1}x - \frac{1}{3}x^3 + \frac{1}{5}x^5 - \frac{1}{7} x^7 + ...
		\end{equation}

		Therefore
		\begin{equation}
			atan(\frac{1}{x}) = \frac{1}{x} - \frac{1}{3x^3} + \frac{1}{5x^5} - \frac{1}{7x^7} + ...
		\end{equation}

		\begin{algorithm}
			\caption{Calculation of $\pi$ using Machin's formula}  
			\label{machin}
			\begin{algorithmic}[1]
				\REQUIRE
				None.
				\ENSURE
				The value of $\pi$ with approximation.
				\RETURN $4[4 atan(1/5) - atan(1/239)]$
			\end{algorithmic}  
		\end{algorithm}

		\begin{algorithm}
			\caption{Calculation of $atan(\frac{1}{x})$}
			\label{atan_inv}
			\begin{algorithmic}[1]
				\REQUIRE x
				\ENSURE $atan(\frac{1}{x})$
				\STATE $ret \gets 0$
				\STATE $e \gets 1/x$
				\STATE $s \gets - x^2$
				\STATE $c \gets 1$
				\WHILE {$e \neq 0$}
				\STATE $ret \gets ret + e/c$
				\STATE $e \gets e/s$
				\STATE $c \gets c + 2$
				\ENDWHILE
				\RETURN ret
			\end{algorithmic}  
		\end{algorithm}

	\newpage

	\item
		The matlab code is given as below.
		\begin{verbatim}
			function [pi] = pi_machin()
			pi = 4*(4*atan_inv(5) - atan_inv(239));

			function [r] = atan_inv(x)
			r = 0;
			e = 1/x;
			s = - x*x;
			c = 1;
			while (e ~= 0)
			r = r + e/c;
			e = e/s;
			c = c+2;
			end
		\end{verbatim}	
\end{enumerate}
